---
title: "Leaflet interactive map"
author: "Sandeep"
date: "July 15, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary
This document will demonstate creation of an interactive map using leaflet library. The data source for the map will come from the {state} datasets that are included in R and which contain data sets related to the 50 states of the United States of America. In particular we will use the following datasets:  

* **state.center**: list with components named x and y giving the approximate geographic center of each state in negative longitude and latitude. Alaska and Hawaii are placed just off the West Coast.
* **state.name**: character vector giving the full state names.
* **state.x77**: Matrix with 50 rows and 8 columns giving state level statistics in the respective columns. We will pick data from following columns:
    * *Population*: population estimate as of July 1, 1975  
    * *Frost*: mean number of days with minimum temperature below freezing (1931-1960) in capital or large city  

##Interactive map
Following is the code that will create the map followed by the map itself:

```{r message=FALSE}
library(leaflet)
state.center%>%
      leaflet()%>%
      addTiles()%>%
      addCircles(lng=state.center$x,lat=state.center$y,
                 popup=state.name,
                 weight=2,
                 radius=sqrt(data.frame(state.x77)$Population)*1000,
                 color=ifelse(data.frame(state.x77)$Frost>120,"red",
                              ifelse(data.frame(state.x77)$Frost>60,
                                     "blue","green")))%>%
      addLegend(labels=c("Frost greater than 120 days",
                         "Frost between 60 and 120 days",
                         "Frost less than 60 days"),
                colors=c("red","blue","green"))
```

##Observations

We can make following observations from the map:  

* There are more circles in the eastern side of US which suggests there are more number of states on the eastern side compared to the western side.
* The circles are bigger on the east and on west coast which suggests that those regions have more population compared to the mid west. 
* The northern states tend to have red circles, southern states have green circles and the region in between have blue circles which suggests that the cold weather becomes less severe when moving from north to south.
